\documentstyle[dream]{article}   
%\documentstyle[a4,dream,equations,TreeTex]{article}   


\begin{document}
\raggedright

\begin{center}
\begin{Large}
{\bf Mathematical Reasoning} \\ [20pt]
\end{Large}
\begin{Huge}
{\bf Formalising Control Knowledge}\\ [20pt]
\end{Huge}
\begin{Large}
{\bf Alan Bundy} 
\end{Large}
\end{center}

\newpage
\begin{huge}
\begin{center} Equation Solving \end{center}
\end{huge}
\begin{LARGE}
\begin{eqnarray*}
\begin{array}{ccc}
\log_{e}(x+1)+\log_{e}(x-1) & = & 3 \\
\log_{e}((x+1).(x-1)) & = & 3 \\
\log_{e}(x^{2}-1) & = & 3 \\
x^{2}-1 & = & e^{3} \\
x^{2} & = & e^{3}+1 \\
x & = & \pm\sqrt{e^{3}+1} \\
\end{array}
\end{eqnarray*}
\end{LARGE}


%
%
%
\newpage
\centerline{\huge \bf Isolation }
\begin{LARGE}
\begin{itemize}
\item [] Example isolation rules:
\begin{eqnarray*}
\log_{V}U=W & \Rightarrow & U=V^{W} \\
U-V=W & \Rightarrow & U=W+V \\
U^{2}=V & \Rightarrow & U=\sqrt{V} \vee U=-\sqrt{V} \\
\end{eqnarray*}
\subitem $U$ is distinguished variable.
\item []
\item [] General format:
\begin{eqnarray*}
f(U_{1},\ldots,U_{i},\ldots,U_{n}) = V \\
\\
\ \ \Rightarrow {\bigvee_{j}}\ [U_{i}=f_{ij}^{-1}(U_{1},\ldots,V,\ldots,U_{n})]
\end{eqnarray*}
\end{itemize}
\end{LARGE}
\newpage

% 
%
%
\centerline{\huge \bf Collection}
\begin{LARGE}
\begin{itemize}
\item [] Example collection rules:
\begin{eqnarray*}
(U+V).(U-V) & \Rightarrow &U^{2}-V^{2} \\
\sin U\,.\,\cos U & \Rightarrow & {1 \over 2}\sin 2.U \\
U.V+U.W & \Rightarrow & U.\,(V+W) \\
\end{eqnarray*}
\subitem $U$ is distinguished variable.
\item []
\item [] General format:
\begin{eqnarray*}
s=t \hbox{ or } s\leftrightarrow t \\
\end{eqnarray*}
\begin{center}
where occ$(U,s)\ >$ occ$(U,t)$, and \\
$s$ least dominating in $U$\\
\end{center}
\end{itemize}
\end{LARGE}
\newpage

%
%
%

\centerline{ \huge \bf Attraction}
\begin{LARGE}
\begin{itemize}
\item [] Example attraction rules:
\begin{eqnarray*}
\log_{W}U+\log_{W}V & \Rightarrow & \log_{W}(U.V) \\
W.U+W.V & \Rightarrow & W.(U+V) \\
(W^{U})^{V} & \Rightarrow & W^{U.V} \\
U^{V.W} & \Rightarrow & (U^V)^W \\
\end{eqnarray*}
\subitem $U$ and $V$ are distinguished variables.
\item []
\item [] General format:
\begin{eqnarray*}
s\lbrack U_{s},V_{s} \rbrack = t\lbrack U_{t},V_{t} \rbrack
\end{eqnarray*}
where
\begin{eqnarray*}
{\rm dist}(U_{s},V_{s},s)>{\rm dist}(U_{t},V_{t},t)
\end{eqnarray*}
\end{itemize}
\end{LARGE}
\newpage


% ****************************************
\begin{center}
\begin{Huge}
{\bf Other Methods}		% Slide Title
\end{Huge}
\end{center}

\begin{LARGE}
\begin{itemize}
\item Simplification.
\item Polynomials.
\item Trigonometric functions.
\item Change of unknown.
\item Homogenization.
\item Factorization.
\end{itemize}
\end{LARGE}
\newpage


% ****************************************
\begin{center}
\begin{Huge}
{\bf Implementation of Methods}		% Slide Title
\end{Huge}
\end{center}

\begin{LARGE}
\begin{itemize}
\item Rewrite rules
\item Multiple rule sets
\item Syntactic characterisation
\item Selective application
\end{itemize}
\end{LARGE}
\end{document}
